An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-06-28 introduction.tex
Update

\section{Introduction}\label{sc:introduction}
Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time. One of the tools used to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature. Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace\cite{Kubler2000}. The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently,
that communicates with each simulation unit via its interface. This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given interval of time. \\
The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface describing how to communicate with each simulation unit. This interface can be used to connect different simulation units (called Functional Mock-up Units or FMUs) and exchange values between them and make them progress in time. \\
A typical co-simulation consists of three phases: Initialization, simulation, and teardown. This work concentrates on the first of these phases - the initialization phase. FMI specifies criteria for how an FMU shall be initialized. However, the FMI standard is not concerned with how a connected system of multiple FMUs should be correctly initialized as a whole. 
The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables. The precedence constraints make specific system configurations and initialization orders of a system invalid due to cyclic dependencies and dependencies among the interconnected variables. An appropriate order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem}. Circular dependencies are important to avoid in a co-simulation scenario since they reduces the ability of a co-simulation to converge \cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.\\

This paper describes an approach for the initialization of an FMI-based co-simulation in linear time of the number of interconnected variables. The approach complies with the semantics of FMI and ensures the absence of cycles in the system. The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation. This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. The approach has been realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2). The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. Gomes et al. have created a co-simulation algorithm generator and verifier\cite{gomes_lucio_vangheluwe_2019} in Prolog an integration to this realization has been crated as a part of the plugin. This integration is used to verify the calculated initialization order against an already established method for calculating the initialization order.\\

>>>>

\section{Introduction}\label{sc:introduction}
Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time. One of the tools used to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature. Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace\cite{Kubler2000}. The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently,
that communicates with each simulation unit via its interface. This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given interval of time. \\
The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface describing how to communicate with each simulation unit. This interface can be used to connect different simulation units (called Functional Mock-up Units or FMUs) and exchange values between them and make them progress in time. \\
A typical co-simulation consists of three phases: Initialization, simulation, and teardown. This work concentrates on the first of these phases - the initialization phase. FMI specifies criteria for how an FMU shall be initialized. However, the FMI standard is not concerned with how a connected system of multiple FMUs should be correctly initialized as a whole. 
The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables. The precedence constraints between the variables can introduce algebraic loops, which places particular requirements on the initialization order since the algebraic loops require a particular initialization strategy to be applied to calculate the initial values. The order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have stabilized at the start of the simulation. Circular dependencies (Algebraic loops) occurs whenever there is an interconnected FMU variable that indirectly depends on itself. Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Kubler2000}. Other approaches for the generation of co-simulation have avoided co-simulation scenarios containing algebraic loops since they reduce the ability of co-simulation to converge \cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}. However, experience has shown that valid co-simulation scenarios containing algebraic loops exist, and a well-established co-simulation framework should be able to handle them. In this work, fixed point iteration techniques have been investigated to initialize scenarios containing algebraic loops properly. The technique is to repeat the evaluation of the output functions of the interconnected variables in each algebraic loop until convergence\cite{Gomes2018}.\\

This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables. The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and ensure convergence of these variables. The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation. This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. The approach has been realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2). The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. Gomes et al. have created a co-simulation algorithm generator and verifier\cite{gomes_lucio_vangheluwe_2019} in Prolog, and an integration to this realization has been created as a part of the work. This integration is used to verify the calculated initialization order against an already established method for calculating the initialization order.\\

### 2020-06-28 paper.tex
Update

\begin{document}
%
\title{An FMI-Based Initialization Plugin for INTO-CPS Maestro 2}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Simon Thrane Hansen\inst{1} \and
Casper Thule\inst{1},
Claudio Gomes \inst{1}}
%
\authorrunning{S. Thrane and C. Thule}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule\}@eng.au.dk\}}}
%
\maketitle              % typeset the header of the contribution
%

@@

\subsection{FMU definitions}
To describe the formalization of FMUs, the vocabulary from Gomes et al\cite{gomes_lucio_vangheluwe_2019, Gomes2018} is adopted. The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information. This paper is only concerned with the initialization-phase of a co-simulation. All information about the time of an FMU and master algorithms is of no relevance and will not be discussed in more detail. 
\begin{definition}[FMU]\label{def:fmu}
  An FMU with identifier $c$ is represented by the tuple   
  $$\tuple{\stateset{c}, \inputs{c}, \outputs{c}, \fset{c}, \fget{c}},$$
  where:
  \begin{inparadesc}
    \item $\stateset{c}$ represents the state space;
    \item $\inputs{c}$ and $\outputs{c}$ the set of input and output variables, respectively;
    \item $\fset{c} : \stateset{c} \times \inputs{c} \times \values \to \stateset{c}$ and $\fget{c}: \stateset{c} \times \outputs{c} \to \values$ are functions to set the inputs and get the outputs, respectively (we abstract the set of values that each input/output variable can take as $\values$).
  \end{inparadesc}
\end{definition}

@@

@@

In the \textit{Initialization Mode} state, the variables of all FMUs should be defined if no circular dependencies exist. 
The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order.

The correct initialization order of these interconnected variables has been calculated using the method described in Gomes et al. \cite{Gomes2019b}. The method is to use a topological ordering as the initialization order. The topological ordering is based on a graph of the interconnected FMU variables and internal connections. 
The calculation of an initialization order can be performed in linear based on the number of both external and internal connections. The calculation should also identify circular dependencies between the interconnected FMU variables since they would invalidate the co-simulation result. This paper's main contribution is to calculate an initialization order of a co-simulation and guarantee absence of cycles in a system being simulated.

\subsection{Structure of the graph}
The graph is constructed based on the interconnected variables and internal connections (feed-through). Each interconnected variable in the system represents a node, and the edges are based on these connections. The edges of this graph represent precedence constraints based on the algebraic dependencies of the interconnected variables. Please see definition \ref{def:initialization_graph} for a formal definition of the graph.

@@

@@

\begin{definition}[Validity criteria for Generation of an Initialization Graph]\label{def:valid_graph}
  The Initialization Graph is valid if the given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$.
  $\forall c \in \fmus \implies \nexists \inputvar{} \in \inputs{c}, \outputvar{} \in \outputs{c}: (\inputvar{},\outputvar{}) \in \feedthrough{c} \land Path(\outputvar{}, \inputvar{})$\\
  Where Paths is defined as the transitive closure of $Path = L \cup \bigcup_{c \in \fmus} \set{\feedthrough{c}}$
\end{definition}

All co-simulation scenarios satisfying definition \ref{def:valid_graph} is guaranteed to have a valid initialization order.

\subsection{Three Tank Example}
The structure of the Initialization Graph will be described using a small example. 
The example is based on three water tanks that are filled and emptied. The first tank is filled from a source with a valve that may be turned on and off. The outflow of the first tank constitutes the inflow of the second, and so forth. A discrete-event controller monitors the level of the third tank and controls a valve to a drain. When the water level of the tank reaches a particular level (defined in the controller), the controller sends a command to the tank to empty using an exit valve. An illustration of the three water tanks can be seen in Figure \ref{fig:watertank}. A diagram of the FMUs showing the interconnections of the FMU variables in the system can be in Figure \ref{fig:watertank}. It should be noted that all internal connections that do not \textit{feed-through} have been omitted to simplify the diagram since they do not influence the initialization order and are not included in the graph defined in definition \ref{def:initialization_graph}.

@@

\begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
  Given an initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ with a finite ordered sequence of FMU function calls $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$ and $i$ denoting the order of the function call. It can be optimized if $\exists \functioncall_i, \functioncall_{i +1} \in \allfunctioncalls : \exists c \in \fmus :(\functioncall_i \in {\fset{c}} \land \functioncall_{i+1} \in {\fset{c}}) \lor (\functioncall_i \in {\fget{c}} \land \functioncall_{i+1} \in {\fget{c}})$
\end{definition}
This optimization uses the fact that the FMI specification allows to \textit{set} or \textit{get} variables of the same FMU to be performed in bulk by grouping interconnected variables of the same FMU with others with similar characteristic.
Since an Initialization procedure is defined in the same they as other co-simulation steps. The optimization process described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step. The only difference between an arbitrary co-simulation step and an initialization procedure is the size of the graph on which the topological sorting is performed. 
The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al. This proof is still valid since this optimization does not change the structure of the Initialization Graph. 
This optimization strategy potentially will not find all valid optimizations of a co-simulation scenario since it works on a co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph. To perform all possible optimizations of a co-simulation step, a more advanced optimization strategy should be used, or the optimization should be performed on the set of all valid co-simulation steps.

@@

\subsection{Topological sorting}
The algorithm for calculating the topological order of the Initialization Graph defined in definition \ref{def:initialization_graph} is Tarjan's algorithm\cite{tarjan_1972}. The algorithm was selected since it solves two of the central issues of the initialization-phase of the co-simulation.
\begin{itemize}
    \item Identifies circular dependencies between interconnected variables (strongly connected components)
    \item Performs a topological sorting of the Initialization Graph
\end{itemize}
The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefan_merz}.

The topological sorting algorithm was implemented in Scala. The choice of Scala is motivated by the relation to JVM and the connection to Slang and the Logika framework\cite{inbook}. The connection to Slang and Logika will be used in the future work of formally verifying the plugin and explore how the contract-based nature of Slang can be used to obtain more trustworthy results of co-simulations.

\subsection{Verification of the approach}
The plugin and the approach behind it have been verified in several different ways. Gomes et al. have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a similar graph to generate not only the initialization order but also the order for a co-simulation master-algorithm. The purpose of the publication by Gomes et al. is a little different from the one of this paper. Gomes et al. are interested in both generating an initialization and master-algorithm, meaning they also need to focus on the time of each FMU. They also define their graph using methods (Set, Get, doStep) instead of interconnected variables, which is the approach described in this paper. This simplification is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU. This does that we can omit all the $doStep$ nodes and all edges connected to them from the graph by Gomes et al., this approach does, therefore, end up with a subgraph of the graph by Gomes et al. The proof from \cite{gomes_lucio_vangheluwe_2019} can therefore trivial be modified to the graph/approach presented in this paper.

The main contribution of Gomes et al. is an implementation of the FMI specification in Prolog freely available to be used in other projects. The Prolog implementation was used in their research to verify their proposed approach for generation of co-simulation algorithms. The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm. As a part of this work, integration from the plugin has been created to the Prolog realization. This integration has been realized in order to verify the correctness of the calculated initialization order against an established and recognized method. The integration is based on JIProlog\cite{}, and it is querying the Prolog database with a co-simulation environment and an initialization order. The integration requires substantially mapping of the objects between the Java code of Maestro 2 and the Prolog implementation, and due to the described differences between the two graphs a mapping from the graph of ports to the graph of operations is needed. This mapping is based on the definitions \ref{def:getout} and \ref{def:setin}.

The Prolog code can generate an initialization order, but this functionality haven't been used for several reasons. The main reason for not generating the initialization order using the Prolog code is based on performance considerations, and the approach taken in this paper does also ensure absence of circular dependencies between the interconnected FMU variables.

\section{Related Work}
Gomes et al. \cite{Gomes2019} propose a strategy for the generation of co-simulation algorithms for FMI-based scenarios based on a graph of the operations of a co-simulation step. However, there are some key differences between their work and ours since the method they purpose does not handle algebraic loops. Furthermore, the approach taken in this paper is only concerned with the initialization procedure of a co-simulation.

The requirement of freedom of algebraic loops of FMI-based co-simulation scenarios to obtain a deterministic composition result of a co-simulation master algorithm was required by Broman et al. \cite{BromanCompositionCo-Simulation}. They proposed to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of a co-simulation step. This insight

Prior work by Amalio et al. \cite{Amalio2016CheckingCo-simulation} has been investigating how to ensure the absence of algebraic loops in FMU based co-simulation scenarios by statically checking the SysML CPS architectural design. The publication's purpose is partly very similar to ours - to guarantee the absence of algebraic loops in a co-simulation scenario. Nevertheless, their approach is only concerned with ensuring the absence of algebraic-loops since their approach is analyzing an architecture design; the calculation of the initialization order is of no interest.

>>>>

\begin{document}
%
\title{An FMI-Based Initialization Plugin for INTO-CPS Maestro 2}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Simon Thrane Hansen\inst{1} \and
Casper Thule\inst{1} \and
Claudio Gomes \inst{1}}
%
\authorrunning{S. Thrane and C. Thule}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule\}@eng.au.dk\}}}
%
\maketitle              % typeset the header of the contribution
%

@@

\subsection{FMU definitions}
To describe the formalization of FMUs, the vocabulary from Gomes et al\cite{gomes_lucio_vangheluwe_2019, Gomes2018} is adopted. The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information. This paper is only concerned with the initialization-phase of a co-simulation. All information about the time of an FMU and master algorithms is of no relevance and will not be discussed in more detail. 
The formalization from Gomes et al. is also extended with some new definitions regarding algrebraic loops, and 
\begin{definition}[FMU]\label{def:fmu}
  An FMU with identifier $c$ is represented by the tuple   
  $$\tuple{\stateset{c}, \inputs{c}, \outputs{c}, \fset{c}, \fget{c}},$$
  where:
  \begin{inparadesc}
    \item $\stateset{c}$ represents the state space;
    \item $\inputs{c}$ and $\outputs{c}$ the set of input and output variables, respectively;
    \item $\fset{c} : \stateset{c} \times \inputs{c} \times \values \to \stateset{c}$ and $\fget{c}: \stateset{c} \times \outputs{c} \to \values$ are functions to set the inputs and get the outputs, respectively (we abstract the set of values that each input/output variable can take as $\values$).
  \end{inparadesc}
\end{definition}

@@

\begin{definition}[Algebraic loops]\todo{Create this definition}
An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
\end{definition}

\begin{definition}[Fixed point iteration]\todo{Create this definition}
An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
\end{definition}

@@

In the \textit{Initialization Mode} state, the variables of all FMUs should be defined if no circular dependencies exist. 
The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order. And an algebraic loop in a co-simulation scenario places even more criteria on the initialization order.

\subsection{Method}
The approach to calculate the initialization order of the interconnected FMU variables are based on the the method proposed in Gomes et al. \cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach used here has been extended with the ability to handle algebraic loops.

\subsubsection{Structure of the graph}
The initialization algorithm starts by building a directed graph of the dependency among the interconnected variables of the FMUs, The graph is constructed based on the interconnected variables and internal connections (feed-through). Each interconnected variable in the system represents a node, and the edges are based on these connections. The edges of this graph represent precedence constraints based on the algebraic dependencies of the interconnected variables. Please see definition \ref{def:initialization_graph} for a formal definition of the graph.

@@

\subsubsection{Calculation of a initialization order}
The topological ordering of a the graph defined in definition \ref{def:initialization_graph} is used a as the initialization order of the interconnected FMU variables. The elements of the topological order is the strongly connected components of the graphs. The strongly connected components are potentially algebraic loops of the system. The algebraic loops is easily identified as the strongly connected components containing more than a single element. The single element members of the topological order is normally interconnected FMU variables, whose value should only be calculated once during the initialization. \\
The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algortihm \cite{tarjan_1972}. Tarjan's algorithm is both detecting the strongly connected components of a graph and calculating the topological ordering.

\todo{Come with an example using a graph with loops}

\subsubsection{Handling of algebraic loops}
As described earlier it is important to handle the algebraic loops by a special strategy since they otherwise would invalidate the result of the co-simulation. The strategy for handling of algebraic loops is to identify and initialize them using a fixed point iteration until the initial value of these converges. The termination of using fixed-point iteration has been proved \todo{Write more}.

This paper's main contribution is to calculate an initialization order of a co-simulation scenario containing algebraic loops. The approach make the circular dependencies between the interconnected converge in the initialization, so the initial values of the interconnected variables in the system being simulated is stable at the time the co-simulation is started.

@@

\begin{definition}[Algebraic loop in an Initialization Graph]\label{def:algebraic_loop}
  An algebraic loop in the given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$ can be found if.\\
  $\exists c \in \fmus : \exists \inputvar{} \in \inputs{c}, \outputvar{} \in \outputs{c}: (\inputvar{},\outputvar{}) \in \feedthrough{c} \land Path(\outputvar{}, \inputvar{})$\\
  Where Path is defined as the transitive closure of $Path = L \cup \bigcup_{c \in \fmus} \set{\feedthrough{c}}$\\
  The algebraic-loops is all \todo{Ask Stefan}
\end{definition}

All co-simulation scenarios satisfying definition \ref{def:algebraic_loop} contains at least one s guaranteed to have a valid initialization order.

\subsection{Case study}
Claduio writes this -section 
\subsection{Three Tank Example}
The structure of the Initialization Graph will be described using a small example. 
The example is based on three water tanks that are filled and emptied. The first tank is filled from a source with a valve that may be turned on and off. The outflow of the first tank constitutes the inflow of the second, and so forth. A discrete-event controller monitors the level of the third tank and controls a valve to a drain. When the water level of the tank reaches a particular level (defined in the controller), the controller sends a command to the tank to empty using an exit valve. An illustration of the three water tanks can be seen in Figure \ref{fig:watertank}. A diagram of the FMUs showing the interconnections of the FMU variables in the system can be in Figure \ref{fig:watertank}. It should be noted that all internal connections that do not \textit{feed-through} have been omitted to simplify the diagram since they do not influence the initialization order and are not included in the graph defined in definition \ref{def:initialization_graph}.

@@

\begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
  Given an initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ with a finite ordered sequence of FMU function calls $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$ and $i$ denoting the order of the function call. It can be optimized if $\exists \functioncall_i, \functioncall_{i +1} \in \allfunctioncalls : \exists c \in \fmus :(\functioncall_i \in {\fset{c}} \land \functioncall_{i+1} \in {\fset{c}}) \lor (\functioncall_i \in {\fget{c}} \land \functioncall_{i+1} \in {\fget{c}})$
\end{definition}
This optimization uses the fact that the FMI specification allows to multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
Since an Initialization procedure is defined in the same they as other co-simulation steps the optimization criteria described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step. The only difference between an arbitrary co-simulation step and an initialization procedure is the size of the dependency graph on which the topological ordering is performed. 
The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al\cite{Gomes2019}. This proof is still valid since this optimization does not change the structure of the Initialization Graph. 
A limitation of using this optimization strategy is that it potentially will not find all valid optimizations of a co-simulation scenario since it works on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph. To perform all possible optimizations of a co-simulation step, a more advanced optimization strategy should be used, or the optimization should be performed on the set of all valid co-simulation steps.

@@

\subsection{Topological sorting}
The algorithm for calculating the topological order of the Initialization Graph defined in definition \ref{def:initialization_graph} is Tarjan's algorithm\cite{tarjan_1972}. The algorithm was selected since it solves two of the central issues of the initialization-phase of the co-simulation.
\begin{itemize}
    \item Identifies circular dependencies between interconnected variables (strongly connected components)
    \item Performs a topological sorting of the Initialization Graph
\end{itemize}
The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefan_merz}. The algorithm is among the best performance graph algorithms to solving the defined task.

The topological sorting algorithm was implemented in Scala. The choice of Scala is motivated by the relation to JVM and the connection to Slang and the Logika framework\cite{inbook}. The connection to Slang and Logika will be investigated in the future. The Logika framework will be used to formally verify the implementation plugin and be used to explore how the contract-based nature of Slang can be used to obtain more reliable results of co-simulations. The topological sorting returns a topological order of strongly connected components. This order is the order of initialization, where the elements containing more than a single element denotes an algebraic loop that requires a particular initialization strategy. The algebraic loops should be initialized using fixed-point iteration in order to obtain a stable initial value.

\subsection{Verification of the approach}
The realized plugin and the developed approach have been verified in several different ways. Gomes et al. have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate not only the initialization order but also the order for a co-simulation master-algorithm. The purpose of the publication by Gomes et al. is a little different from the one of this paper. Gomes et al. are interested in both generating an initialization and master-algorithm, meaning they also need to focus on the time of each FMU. They also define their graph using methods (Set, Get, doStep) instead of interconnected variables, which is the approach described in this paper. This simplification is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU. This does that we can omit all the $doStep$ nodes and all edges connected to them from the graph by Gomes et al., this approach does, therefore, end up with a subgraph of the graph by Gomes et al. The proof from \cite{gomes_lucio_vangheluwe_2019} can therefore trivial be modified to the graph/approach presented in this paper.

Gomes et al. 's main contribution is an implementation of the FMI specification in Prolog freely available to be used in other projects. The Prolog implementation was used in their research to verify their proposed approach for the generation of co-simulation algorithms. The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm. As a part of this work, an integration from this plugin has been realized to interact with the Prolog realization. This integration has been realized in order to verify the correctness of the calculated initialization order against an established and recognized method. The integration is based on JIProlog\cite{}, and it is querying the Prolog database with a co-simulation environment and an initialization order. The integration requires substantial mapping of the objects between the Java code of Maestro 2 and the Prolog implementation. Due to the described differences between the two graphs, a mapping from the graph of ports to the graph of operations is needed. This mapping is based on the definitions \ref{def:getout} and \ref{def:setin}.

The Prolog code can generate an initialization order, but this functionality has not been used for several reasons. The main reason for not generating the initialization order using the Prolog code is based on performance considerations. The approach taken in this paper does also identifies the strongly connected components and performs a particular initialization strategy of these.

\section{Related Work}
Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} had been looking into the generation of co-simulation algorithms for both master and initialization algorithms for FMI-based scenarios based on a graph of the operations of a co-simulation step. Gomes and Broman do both present an approach where they use the topological sorting of a dependency graph to establish a correct order in which the operations of a co-simulation step should be performed. 
Gomes et al. \cite{Gomes2019} propose a strategy for the generation of co-simulation algorithms and define the criteria for a correct co-simulation step.  Their work has many similarities with ours. However, their work is not implemented and used in a practical context like ours that has been implemented as a plugin to Maestro 2. Furthermore, the approach taken in this paper is only concerned with the initialization procedure of a co-simulation.

The work by Broman et al. \cite{BromanCompositionCo-Simulation} proposes using the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations. Nevertheless, they specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a deterministic co-simulation algorithm. It means they refuse all co-simulation scenarios containing algebraic loops. This is a significant difference in our approach. The approach in this paper is more specialized in the sense that it is only considering the initialization of a co-simulation. This focus does that our work do need to include the handling of non-interconnected variables that should be addressed during the initialization of a co-simulation.

Prior work by Amalio et al. \cite{Amalio2016CheckingCo-simulation} has been investigating how to find and avoid algebraic loops in FMU based co-simulation scenarios by statically checking the SysML CPS architectural design. The publication's purpose is a bit different from ours - to guarantee the absence of algebraic loops in a co-simulation scenario. But their approach of being implemented 
Nevertheless, their approach is only concerned with ensuring the absence of algebraic-loops since their approach is analyzing an architecture design; the calculation of the initialization order is not in scope of their work.
